Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-11-17 jessie-writeup/jessie-writeup.tex
In writeup, tried to start writing a statement about smoothness of embeddable functions.  Added Mathematica file to generate examples, but I think something's wrong in it.

>>>>

\newpage
\begin{conjecture}\label{conj:embeds-finite-iff-nonsmooth}
	Let $\Gamma$ be a property elicited by the \jessie{convex?} loss $L$.
	Then $\Gamma$ embeds a finite property $\gamma$ $\iff$ the loss $L(r,y)$ is nonsmooth for all $y \in \Y$.  \jessie{define later: in the convex hull of sensible reports}.
\end{conjecture}
\begin{proof}
	We rely on the observation that over finite outcomes, $\Gamma(p) \in \argmin_r \E_p L(r,Y) \iff 0 \in \partial_r \E_p L(\Gamma(p), Y)$.

	For the forward direction, we know that if $\Gamma$ embeds a finite property, then there must be a finite set $\R'$ so that for all $p \in \P$, $\exists r \in \R'$ so that $r \in \Gamma(p)$.
	This is achieved by an FPLC, which is nonsmooth.

	For the reverse implication, we try a contradiction.
	Suppose there was some outcome $z \in \Y$ so that $L(r,z)$ is smooth over $\R$.
	We can rewrite the expected loss as follows:
	\begin{align*}
		\E_p L(r,Y) &= \sum_{y \in \Y} p(y) L(r, y) \\
		&= \sum_{y\neq z \in \Y} p(y) L(r, y) + p(z) L(r,z) \\
		&= (1-p(z))\sum_{y\neq z \in \Y} \frac{p(y)}{1-p(z)} L(r, y) + p(z) L(r,z) \\
		&= (1-p(z))\bar L(r,p) + p(z) L(r,z) \\
	\end{align*}
	where $\bar L(r,p) := \sum_{y\neq z \in \Y} \frac{p(y)}{1-p(z)} L(r,y)$.
	Now, assume there are distributions $p, q \in \P$ such that there is no $r' \in \R$ such that $r' \in \argmin_r \E_pL(r,Y) \cap \argmin_r \E_q L(r,Y)$.
	Let $r_1, r_2 \in \R$ such that $0 \in \partial_r \E_p L(r_1, Y)$ and $0 \in \partial_r \E_q L(r_2, Y)$. 
	For any $\lambda \in [0,1]$
	\begin{align*}
		\partial_r \E_p L(r', Y) + \partial_r \E_q L(r, Y) \neq 0.		
		\implies \partial_r \bar L(r', p) + p(z) \partial_r L(r',z)  + \partial_r \tilde L(r, q) + q(z) \partial_r L(r',z) \neq 0\\
		\implies 
%		\lambda[\partial_r \bar L(r) + p(z) \partial_r L(r,z)] + (1-\lambda) [\partial_r \tilde L(r) + q(z) \partial_r L(r,z)] = 0
	\end{align*}
\end{proof}
